Language-Based Low-Level MPC Security: $\metaprot$ to $\minifed$

### 2024-05-05 ppdp24/hyper.tex
checkpoint

In fact, MPC protocols typically satisfy a \emph{delimited release}
property\cite{sabelfeld2009declassification}, where messages exchanged remain probabilistically separable
from secrets, with only declassification events (reveals and outputs)
releasing information about honest secrets. A key difference is that while
these declassification events essentially define the policy in delimited
release, the ideal functionality sets the release policy for MPC
passive security, so its necessary to show that declassification events respect
these bounds.
\begin{definition}
  Given $H,C$, a protocol $\prog$ with $\iov(\prog) = S \cup M \cup P \cup O$
  satisfies \emph{delimited release} iff
  $\sep{\progtt(\prog)}{M_C}{S_H}$.
\end{definition}

>>>>

In practice, MPC protocols typically satisfy a \emph{delimited release}
property \cite{sabelfeld2009declassification}, where messages exchanged remain probabilistically separable
from secrets, with only declassification events (reveals and outputs)
releasing information about honest secrets. A key difference is that while
these declassification events essentially define the policy in delimited
release, the ideal functionality sets the release policy for MPC
passive security, so its necessary to show that declassification events respect
these bounds.
\begin{definition}
  Given $H,C$, a protocol $\prog$ with $\iov(\prog) = S \cup M \cup P \cup O$
  satisfies \emph{delimited release} iff
  $\sep{\progtt(\prog)}{M_C}{S_H}$.
\end{definition}
